---
title: "Power Study"
author: "Alexey Luchinsky"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
rm(list = ls())
```


# Table V

```{r}
source("./scripts/Tab5.R")
```


## Trying to reproduce Table V from the article



```{r}
alpha.list <- c(0.01, 0.02, 0.05, 0.1, 0.2) 
n.list <- c(10, 20, 50, 100, 200, 500)
```

Calculate the CVs. It takes about 5 mins to do 10 loops. Change to true if you want to update the statistacs

```{r}
if(FALSE) {
  system.time({
    for(n in n.list) {
      print(paste("n=", n))
      df <- updateJBCVfile(n = n, alpha = alpha.list, nLoop = 10)
    }
  })
}
df <- readRDS("../data/processed/tab5.rds")
```

```{r}
df
```


```{r}
df %>% group_by(n, alpha) %>% summarise(num = n())
```


```{r}
df %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) 
```


Making table:

```{r}
df %>% filter(n %in% n.list) %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% 
  tidyr::spread(n, cv) %>% round(3)
```

Reading table from paper

```{r}
# conversion done with https://pdftables.com/blog/convert-pdf-to-csv
paper.data <- read.csv("../data/external/Table5.csv")
Tab5 <- paper.data
colnames(Tab5)= c("alpha", "10", "20", "50", "100", "200", "500", "1000")
Tab5_long <- gather(Tab5, key = n, value = cv, "10":"1000")
Tab5_long$n <- as.numeric(Tab5_long$n)
Tab5_long %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% spread(n, cv) %>% round(3)
```

All plots on one axes frame:

```{r}
df %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% 
  ggplot(aes(x=n, y=cv, group = alpha, color = factor(alpha))) + geom_line() +
    geom_point(data = Tab5_long, aes(x=n, y = cv, group = alpha, color = as.factor(alpha)), cex = 2) + 
  scale_x_log10() +
  ggtitle("Comparison of the calculation (line) with paper's Table 5 (article)")
```

As facet grid

```{r}
df %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% 
  ggplot(aes(x=n, y=cv)) + geom_line() + 
  geom_point(data = Tab5_long, aes(x=n, y = cv, group = alpha, color = as.factor(alpha)), cex = 2) + 
  scale_x_log10() +
  facet_wrap(~ alpha)
```

Using grid.arrange



```{r fig.height=5, fig.width=5}
figs = list()
for(i in 1:length(alpha.list)) {
  alpha_ <- alpha.list[i]
  figs[[i]] <- df %>% filter(alpha == alpha_) %>% group_by(n) %>% summarise(cv = mean(cv)) %>% 
    ggplot(aes(x = n, y = cv)) + geom_line() +
    geom_point(data = Tab5_long %>% filter(alpha == alpha_), aes(x=n, y = cv), cex = 2, color = "red") + 
    scale_x_log10() +
    ggtitle(paste("Comparison with Table 5, alpha = ", alpha_))
}
gridExtra::grid.arrange(grobs = figs)
```
## Figures

```{r}
set.seed(123)
n <- 20
N <- 1e5
alpha <- 0.2
data <- matrix(rnorm(n*N), ncol = n)
T <- apply(data, 1,function(x) tseries::jarque.bera.test(x)$statistic)
t0 <- quantile(T, 1-alpha)
#MASS::truehist(T, main = paste("n=", n," alpha=",alpha, " t0=", round(t0,3)), xlim=c(0,12), ylim = c(0, 0.7))
```

```{r}
par(pty="s")
MASS::truehist(T, main = paste("n=", n," alpha=",alpha, " t0=", round(t0,3)), xlim=c(0,12), ylim = c(0, 0.7))
curve(dchisq(x, 2), add=TRUE, col="red", lty=4, lwd=3)
grid()
legend("topright", legend = c(paste("n=",n), "inf"), lty=c(1, 4), col=c("black", "red"))
```

# Table VI

```{r}
source("scripts/Tab6.R")
```


Generating critical values for specific n and saving it to the file. Note that this command can take long to run

```{r}
if(FALSE) {
  ntry <- 100
  pb <- knitrProgressBar::progress_estimated(ntry)
  for(i in 1:ntry) {
    knitrProgressBar::update_progress(pb)
    df <- saveTab6(n=5, ne = 1e4)
  }
}
df <- readRDS("../data/processed//tab6.rds")
```



```{r}
df <- readRDS("../data/processed//tab6.rds")
df %>% group_by(n) %>% summarise(nn = n())
```

```{r}
n.list
```


```{r}
df %>% filter(n %in% n.list) %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% tidyr::spread(n, cv) %>% round(3)
```



```{r}
Tab6 <- read.csv("../data/external/Table6.csv")
colnames(Tab6) = c("alpha", "10", "20", "50", "100", "200", "500")
Tab6_long <- gather(Tab6, key = n, value = cv, "10":"500")
Tab6_long$n <- as.numeric(Tab6_long$n)
Tab6
```



```{r}
df %>% group_by(n, alpha) %>% summarize(cv = mean(cv), .groups = "drop") %>% 
  ggplot(aes(x=n, y=cv, group = alpha, colour = factor(alpha))) + geom_line() + geom_point(cex=0.7) +
  geom_point(data = Tab6_long, aes(x=n, y = cv, group = alpha, color = as.factor(alpha)), cex = 2) + 
  ggtitle("Comparison of the calculation (line) with paper's Table 6 (article)")
```

## intervals


```{r}
library(boot)
```

```{r}
alpha_ <- 0.01
n_ <- 500
data <- df %>% filter(n == n_ & alpha == alpha_) %>% pull(cv)
boot.out <- boot(data, function(x, ind) mean(x[ind]), R = 999)
ci <- boot.ci( boot.out, type = "bca")
list(
  paper = Tab6[Tab6[,1] == alpha_, colnames(Tab6)==n_],
  my = ci$bca[4:5]
)
```

# Table 8

```{r}
source("scripts/tabSK.R")
```

 
Testing:

```{r}
set.seed(123)
x <- genFCN(1e5, p = 0.8, mu2 = 4, sigma2 = 1)
MASS::truehist(x, ylab = "F", xlab = "x", main = "p=0.8, mu2 = 4, sigma2 = 1" )
curve( (1-0.8)*dnorm(x) + 0.8*dnorm(x, mean=4, sd=1), add = TRUE, col="red", lwd = 2)
```

This library is used to calculate easily skewness and kurtosis os the sample


type = 1 choice is in agreement with the article's conventions (note that you should subtract 3 from the kurtosis)

```{r}
mx <- mean(x)
c( 
  mean( (x-mx)**3)/mean( (x-mx)^2)^(3/2),
  skewness(x, type = 1)
)
c(
  mean((x-mx)^4)/mean( (x-mx)^2)^2,
  3+kurtosis(x, type=1)
)
```

```{r}
df <- data.frame()
```

I put the time consuming lines under `if(FALSE) {}` to prevant automatic evaluation. It can be easily evaluated by selecting the inner code and pressing Cmd-Enter (on Mac)

```{r}

if(FALSE) {
  for( sigma2 in c(1,2,3,4,6)) {
    df <- saveSKtable(p = 0.5, mu2 = 3, sigma2 = sigma2)
  }
}
```


```{r}
df <- readRDS("../data/processed/tabSK.rds")
df %>% filter(mu2 >0 ) %>% 
  group_by(p, mu2, sigma2) %>% summarize(Sk = mean(Sk), Kurt = mean(Kurt)) %>% round(2)
```


```{r}
boot.out <- boot(df$Kurt, function(x, ind) mean(x[ind]), 999)
boot.out
```

```{r}
boot.ci(boot.out)
```

