---
title: "Power Study"
author: "Alexey Luchinsky"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
rm(list = ls())
```


# Table V

```{r}
source("./scripts/Tab5.R")
```


## Trying to reproduce Table V from the article



```{r}
alpha.list <- c(0.01, 0.02, 0.05, 0.1, 0.2) 
n.list <- c(10, 20, 50, 100, 200, 500)
```

Calculate the CVs. It takes about 5 mins to do 10 loops. Change to true if you want to update the statistacs

```{r}
if(FALSE) {
  system.time({
    for(n in n.list) {
      print(paste("n=", n))
      df <- updateJBCVfile(n = n, alpha = alpha.list, nLoop = 10)
    }
  })
}
df <- readRDS("../data/processed/tab5.rds")
```

```{r}
df
```


```{r}
df %>% group_by(n, alpha) %>% summarise(num = n())
```


```{r}
df %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) 
```


Making table:

```{r}
df %>% filter(n %in% n.list) %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% 
  tidyr::spread(n, cv) %>% round(3)
```

Reading table from paper

```{r}
# conversion done with https://pdftables.com/blog/convert-pdf-to-csv
paper.data <- read.csv("../data/external/Table5.csv")
Tab5 <- paper.data
colnames(Tab5)= c("alpha", "10", "20", "50", "100", "200", "500", "1000")
Tab5_long <- gather(Tab5, key = n, value = cv, "10":"1000")
Tab5_long$n <- as.numeric(Tab5_long$n)
Tab5_long %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% spread(n, cv) %>% round(3)
```

All plots on one axes frame:

```{r}
df %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% 
  ggplot(aes(x=n, y=cv, group = alpha, color = factor(alpha))) + geom_line() +
    geom_point(data = Tab5_long, aes(x=n, y = cv, group = alpha, color = as.factor(alpha)), cex = 2) + 
  scale_x_log10() +
  ggtitle("Comparison of the calculation (line) with paper's Table 5 (article)")
```

As facet grid

```{r}
df %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% 
  ggplot(aes(x=n, y=cv)) + geom_line() + 
  geom_point(data = Tab5_long, aes(x=n, y = cv, group = alpha, color = as.factor(alpha)), cex = 2) + 
  scale_x_log10() +
  facet_wrap(~ alpha)
```

Using grid.arrange



```{r fig.height=5, fig.width=5}
figs = list()
for(i in 1:length(alpha.list)) {
  alpha_ <- alpha.list[i]
  figs[[i]] <- df %>% filter(alpha == alpha_) %>% group_by(n) %>% summarise(cv = mean(cv)) %>% 
    ggplot(aes(x = n, y = cv)) + geom_line() +
    geom_point(data = Tab5_long %>% filter(alpha == alpha_), aes(x=n, y = cv), cex = 2, color = "red") + 
    scale_x_log10() +
    ggtitle(paste("Comparison with Table 5, alpha = ", alpha_))
}
gridExtra::grid.arrange(grobs = figs)
```
## Figures

```{r}
set.seed(123)
n <- 20
N <- 1e5
alpha <- 0.2
data <- matrix(rnorm(n*N), ncol = n)
T <- apply(data, 1,function(x) tseries::jarque.bera.test(x)$statistic)
t0 <- quantile(T, 1-alpha)
#MASS::truehist(T, main = paste("n=", n," alpha=",alpha, " t0=", round(t0,3)), xlim=c(0,12), ylim = c(0, 0.7))
```

```{r}
par(pty="s")
MASS::truehist(T, main = paste("n=", n," alpha=",alpha, " t0=", round(t0,3)), xlim=c(0,12), ylim = c(0, 0.7))
curve(dchisq(x, 2), add=TRUE, col="red", lty=4, lwd=3)
grid()
legend("topright", legend = c(paste("n=",n), "inf"), lty=c(1, 4), col=c("black", "red"))
```

# Table VI

```{r}
source("scripts/Tab6.R")
```


Generating critical values for specific n and saving it to the file. Note that this command can take long to run

```{r}
if(FALSE) {
  ntry <- 100
  pb <- knitrProgressBar::progress_estimated(ntry)
  for(i in 1:ntry) {
    knitrProgressBar::update_progress(pb)
    df <- saveTab6(n=5, ne = 1e4)
  }
}
df <- readRDS("../data/processed//tab6.rds")
```



```{r}
df <- readRDS("../data/processed//tab6.rds")
df %>% group_by(n) %>% summarise(nn = n())
```

```{r}
n.list
```


```{r}
df %>% filter(n %in% n.list) %>% group_by(n, alpha) %>% summarise(cv = mean(cv)) %>% tidyr::spread(n, cv) %>% round(3)
```



```{r}
Tab6 <- read.csv("../data/external/Table6.csv")
colnames(Tab6) = c("alpha", "10", "20", "50", "100", "200", "500")
Tab6_long <- gather(Tab6, key = n, value = cv, "10":"500")
Tab6_long$n <- as.numeric(Tab6_long$n)
Tab6
```



```{r}
df %>% group_by(n, alpha) %>% summarize(cv = mean(cv), .groups = "drop") %>% 
  ggplot(aes(x=n, y=cv, group = alpha, colour = factor(alpha))) + geom_line() + geom_point(cex=0.7) +
  geom_point(data = Tab6_long, aes(x=n, y = cv, group = alpha, color = as.factor(alpha)), cex = 2) + 
  ggtitle("Comparison of the calculation (line) with paper's Table 6 (article)")
```

## intervals


```{r}
library(boot)
```

```{r}
alpha_ <- 0.01
n_ <- 500
data <- df %>% filter(n == n_ & alpha == alpha_) %>% pull(cv)
boot.out <- boot(data, function(x, ind) mean(x[ind]), R = 999)
ci <- boot.ci( boot.out, type = "bca")
list(
  paper = Tab6[Tab6[,1] == alpha_, colnames(Tab6)==n_],
  my = ci$bca[4:5]
)
```

# Table 8

```{r}
source("scripts/tabSK.R")
```

 
Testing:

```{r}
set.seed(123)
x <- genFCN(1e5, p = 0.8, mu2 = 4, sigma2 = 1)
MASS::truehist(x, ylab = "F", xlab = "x", main = "p=0.8, mu2 = 4, sigma2 = 1" )
curve( (1-0.8)*dnorm(x) + 0.8*dnorm(x, mean=4, sd=1), add = TRUE, col="red", lwd = 2)
```

This library is used to calculate easily skewness and kurtosis os the sample


type = 1 choice is in agreement with the article's conventions (note that you should subtract 3 from the kurtosis)

```{r}
mx <- mean(x)
c( 
  mean( (x-mx)**3)/mean( (x-mx)^2)^(3/2),
  skewness(x, type = 1)
)
c(
  mean((x-mx)^4)/mean( (x-mx)^2)^2,
  3+kurtosis(x, type=1)
)
```

```{r}
df <- data.frame()
```

I put the time consuming lines under `if(FALSE) {}` to prevant automatic evaluation. It can be easily evaluated by selecting the inner code and pressing Cmd-Enter (on Mac)

```{r}

if(FALSE) {
  # Table 8
#  for( sigma2 in c(1,2,3,4,6)) {
#    df <- saveSKtable(p = 0.5, mu2 = 3, sigma2 = sigma2)
#  }
  # Table 9
#  for(mu2 in c(0, 1, 2, 3, 4)) {
#    df <- saveSKtable(p = 0.50, mu2 = mu2, sigma2 = 1)
#  }
  for(p in c(0.05, 0.20, 0.5, 0.8, 0.95)) {
    df <- saveSKtable(p = p, mu2 = 0, sigma2 = 4) 
  }
}
```


```{r}
df <- readRDS("../data/processed/tabSK.rds")
df %>% filter(sigma2 == 4 & mu2 == 0 ) %>% 
  group_by(p, mu2, sigma2) %>% summarize(Sk = mean(Sk), Kurt = mean(Kurt)) %>% round(2)
```


```{r}
boot.out <- boot(df$Kurt, function(x, ind) mean(x[ind]), 999)
boot.out
```

```{r}
boot.ci(boot.out)
```

# Figures

## Data Collection

```{r}
source("./scripts/tabSK.R")
```


```{r}
df<- readRDS("../data/processed/tabPower.rds")
calcPower <- function(n = 100, p = 0.1, mu2 = 0, sigma2 = 1, alpha = 0.05,
                      file_name = "../data/processed/tabPower.rds") {
  if( !file.exists(file_name)) {
    df <- data.frame()
  } else {
    df <- readRDS(file_name)
  }
  n_ <- n;
  alpha_ <- alpha;
  t0 <- filter(df5, n == n_ & alpha == alpha_)
  if(nrow(t0) == 0) {
    t0 <- as.numeric( getJBCV(n = n, alpha = alpha) )
  }
  else {
    t0 <- as.numeric( mean(t0$cv))
  }
  T <- replicate(1e4, {
    z <- genFCN(n = n, p = p, mu2 = mu2, sigma2 = sigma2)
    tseries::jarque.bera.test(z)$statistic
  })
  df <- rbind(df, 
            data.frame(n = n, p = p, mu2 = mu2, sigma2 = sigma2, alpha = alpha, P = mean(T > t0))
            )
  saveRDS(df, file_name)
  df
}
```



```{r}
if(FALSE) {
  sigma2.list <- seq(1, 6, 0.5)
  pb <- knitrProgressBar::progress_estimated( length(mu2.list))
  for( sigma2 in sigma2.list) {
    knitrProgressBar::update_progress(pb)
    df <- calcPower(n = 100, mu2 = 0, p = 0.50, sigma2 = sigma2)
  }
}
```




## Fig 5

```{r}
fig5_true <- read.csv("../data/external/Fig5.csv", header = FALSE, col.names = c("sigma2", "P"))
n <- 100
mu2 <- 0
p <- 0.10
df %>% filter(n==100 & mu2 == 0 & p == 0.10) %>% 
  ggplot(aes(x=sigma2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 1) + geom_hline(yintercept = 0.05, lty=2) +
  geom_point( data = fig5_true, aes(x = sigma2, y = P), color = "red", cex = 3) +
  labs(x = "sigma2", title = paste("Fig5: n=", n," mu2=", mu2, "p=",p))
rm(n, mu2, p)
```

```{r}
n_ = 100
mu2_ = 0
p_ = 0.1
sigma2.list <- seq(0.1, 6, 0.1)
pb <- knitrProgressBar::progress_estimated( length(sigma2.list))
JBpower <- sapply(sigma2.list, function(sigma2_) { 
  knitrProgressBar::update_progress(pb)
  P <- replicate(1e4, {
    z <- genFCN(n = n_, p = p_, mu2 = mu2_, sigma2 = sigma2_)
    tseries::jarque.bera.test(z)$p.value
  })
  mean(P < 0.05)
  })
```

```{r}
fig5_true <- read.csv("../data/external/Fig5.csv", header = FALSE, col.names = c("sigma2", "P"))
data_frame(sigma2 = sigma2.list, P = JBpower) %>% 
  ggplot(aes(x = sigma2, y = P)) + geom_line() +
  geom_point( data = fig5_true, aes(x = sigma2, y = P), color = "red", cex = 3) +
  geom_hline(yintercept = 0.05, lty=2) + geom_vline(xintercept = 1, lty = 2) +
  ggtitle(paste("Fig 5: n=", n_, " mu2 = ", mu2_, " p=", p_))

```


```{r}
plot(sigma2.list, JBpower)
```


## Fig 6

```{r}
n_ = 100
mu2_ = 0
p_ = 0.50
sigma2.list <- seq(0.1, 6, 0.1)
pb <- knitrProgressBar::progress_estimated( length(sigma2.list))
JBpower <- sapply(sigma2.list, function(sigma2_) { 
  knitrProgressBar::update_progress(pb)
  P <- replicate(1e4, {
    z <- genFCN(n = n_, p = p_, mu2 = mu2_, sigma2 = sigma2_)
    tseries::jarque.bera.test(z)$p.value
  })
  mean(P < 0.05)
  })
```


```{r}
fig6_true <- read.csv("../data/external/Fig6.csv", header = FALSE, col.names = c("sigma2", "P"))
n_ <- 100
mu2_ <- 0
p_ <- 0.50
df %>% filter(n==n_ & mu2 == mu2_ & p == p_) %>% 
  ggplot(aes(x=sigma2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 1) + geom_hline(yintercept = 0.05, lty=2) +
  geom_point( data = fig6_true, aes(x = sigma2, y = P), color = "red", cex = 3) +
  labs(x = "sigma2", title = paste("Fig6: n=", n_," mu2=", mu2_, "p=",p_))
rm(n_, mu2_, p_)
```


## Fig 7


```{r}
n_ <- 200
mu2_ <- 0
fig7_true <- read.csv("../data/external/Fig7.csv", header = FALSE, col.names = c("sigma2", "P"))
df %>% filter(n==n_ & mu2 == mu2_) %>% group_by(sigma2) %>% summarise(P = mean(P)) %>% 
ggplot(aes(x=sigma2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 1) + geom_hline(yintercept = 0.05, lty=2) +
  geom_point( data = fig7_true, aes(x = sigma2, y = P), color = "red", cex = 3) +
  labs(x = "sigma2", title = paste("Figs 7: n=", n_," mu2=", mu2_))
```

## Fig 8



```{r}
n_ <- 50
mu2_ <- 3
p_ <- 0.50
fig8_true <- read.csv("../data/external/Fig8.csv", header = FALSE, col.names = c("sigma2", "P"))
df %>% filter(n==n_ & mu2 == mu2_ & p == p_) %>% group_by(sigma2) %>% summarise(P = mean(P)) %>% 
ggplot(aes(x=sigma2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 1) + geom_hline(yintercept = 0.05, lty=2) +
  geom_point( data = fig8_true, aes(x = sigma2, y = P), color = "red", cex = 3) +
  labs(x = "sigma2", title = paste("Figs 8: n=", n_," mu2=", mu2_, " p=", p_))
```


## Fig 9

```{r}
n_ <- 50
p_ <- 0.05
sigma2_ <- 4
fig9_true <- read.csv("../data/external/Fig9.csv", header = FALSE, col.names = c("mu2", "P"))
df %>% filter(n==n_ & sigma2 == sigma2_) %>% group_by(mu2) %>% summarise(P = mean(P)) %>% 
ggplot(aes(x=mu2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_point( data = fig9_true, aes(x = mu2, y = P), color = "red", cex = 3) +
  ggtitle( paste("Figs 9: n=", n_," sigma2=", sigma2_, " p=", p_)) +
  ylim(c(0,1))
```

## Fig 10

```{r}
n_ <- 50
p_ <- 0.50
sigma2_ <- 1
fig10_true <- read.csv("../data/external/Fig10.csv", header = FALSE, col.names = c("mu2", "P"))
df %>% filter(n==n_ & sigma2 == sigma2_) %>% group_by(mu2) %>% summarise(P = mean(P)) %>% 
ggplot(aes(x=mu2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_point( data = fig10_true, aes(x = mu2, y = P), color = "red", cex = 3) +
  ggtitle( paste("Figs 10: n=", n_," sigma2=", sigma2_, " p=", p_)) +
  ylim(c(0,1))
```

## Fig 11

```{r}
n_ <- 50
mu2_ <- 0
sigma2_ <- 4
fig11_true <- read.csv("../data/external/Fig11.csv", header = FALSE, col.names = c("p", "P"))
df %>% filter(n==n_ & mu2 == mu2_ & sigma2 == sigma2_) %>% 
  ggplot(aes(x=p, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 0) + geom_hline(yintercept = 0.05, lty=2) +
  geom_point( data = fig11_true, aes(x = p, y = P), color = "red", cex = 3) +
  labs(x = "p", title = paste("Figs 11: n=", n_," mu2=", mu2_, "sigma2 = ", sigma2_))
```

## Fig 12

```{r}
tail(df)
```


```{r}
n_ <- 100
mu2_ <- 0
p_ <- 0.50
fig12_true <- read.csv("../data/external/Fig12.csv", header = FALSE, col.names = c("sigma2", "P"))
df %>% filter(n==n_ & mu2 == mu2_ & p == p_) %>% group_by(sigma2) %>% summarise(P = mean(P)) %>% 
ggplot(aes(x=sigma2, y=P)) + geom_line() + geom_point() + geom_point() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 1) + geom_hline(yintercept = 0.05, lty=2) +
  geom_point( data = fig12_true, aes(x = sigma2, y = P), color = "red", cex = 3) +
  labs(x = "sigma2", title = paste("Figs 8: n=", n_," mu2=", mu2_, " p=", p_))
```
